Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
fix table V

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}. \Mar{igor,
  nao consigo entender o porque deste caso nao dar aqueles erros
  (ReferenceError/TypeError) que vc. me mostrou e estourar na
  assercao. explique e de um exemplo concreto, por favor$\rightarrow$
}
\Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
diferente da que usamos anteriormente. Por exemplo, existem testes que 
estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
}
\textbf{Non-Standard Element.} This kind corresponds to the cases the
test case relies on some non-standard function or property of a
standard object. \Mar{igor, ha alguma explicacao/intuicao para
  explicar porque nao conseguir classificar
  isto?.$\rightarrow$}
  \Igor{Exemplos: Testes especificos do engenho que }
  \textbf{Unknown.} This category includes the
cases we were unable to confidently diagnose the failure but we
suspected it was a false alarm.

@@

\begin{table}[h!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 177 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}
\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
alterar o corpo da mensagem. Esta era a ideia, mas 
}

>>>>

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}. \Mar{igor,
  nao consigo entender o porque deste caso nao dar aqueles erros
  (ReferenceError/TypeError) que vc. me mostrou e estourar na
  assercao. explique e de um exemplo concreto, por favor$\rightarrow$
}
\Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
diferente da que usamos anteriormente. Por exemplo, existem testes que 
estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
}
\textbf{Non-Standard Element.} This kind corresponds to the cases the
test case relies on some non-standard function or property of a
standard object. \Mar{igor, ha alguma explicacao/intuicao para
  explicar porque nao conseguir classificar
  isto?.$\rightarrow$}
  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
  por exemplo cobre uma especificacao antiga onde o
  teste esperava uma propriedade true, mas na documentacao 
  cita que a propriedade tem que ser false.}
  \textbf{Unknown.} This category includes the
cases we were unable to confidently diagnose the failure but we
suspected it was a false alarm.

@@

\begin{table}[h!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}
\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
alterar o corpo da mensagem. Esta era a ideia, mas 
casos onde o fuzzer muda a msg em uma assercao 
(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")') 
todos os engenhos falham e o teste nao ser reportado caso alcance esse bloco.
Porem, existem casos em que o teste falha por message mismatch, 
mas a discrepancia ocorre no engenho que nao exibe essa mensagem. 
Analisando os casos que encontramos dessa natureza, 
a comparacao da mensagem aparece no report, 
porem a discrepancia ocorre quando o teste nao mostra 
essa mensagem (passa por motivos de invalid input). 
Eu classifiquei como message mismatch, 
mas creio que nesse caso seria invalid input. Pq se for message mis
}
